### 2020-10-16 doc/manuscript/Dow_manuscript.Rmd
added climwin figure (sketch), worked on manuscript

#Figure numbers
schematic=1 #Based on D'Orangeville Figure 1
growth_pheno_by_xylem = 2
rel_growth = "2a" #Based on D'Orangeville Figure 3.a), but with relative growth
cum_growth = "2b" #Similar to D'Orangeville Figure 4.a), but with cumulative relative growth
# 3 climwin

pheno_Tsensitivity = 4

@@

@@

@@

•	Sean’s model

•	Climwin

*Analysis*

@@

@@

•	variable averages

Pooled across all species and all years the average DOY where max growth rate was achieved is DOY: 158, the DOY where 25% was achieved is DOY: 129, 50% - DOY: 157, 75% - DOY:184.

@@

Across all trees, Pooled across all species and all years the average DOY where max growth rate was achieved is DOY: 158, the DOY where 25% was achieved is DOY: 129, 50% - DOY: 157, 75% - DOY:184.

Growth pheonology differed between ring- and diffuse- porous species, with ring-porous species having an earlier start to growth, with growth spread out over a longer growing season (Fig. `r growth_pheno_by_xylem`).
Specifically,

Ring-porous (1395 obs) max growth rate – DOY: 147, max growth rate = .048 (find units in Sean’s function), 25% - DOY: 113, 50% DOY: 147, 75% - DOY: 181…68 days

Diffuse-porous (993 obs) max growth rate – DOY: 172, max growth rate = .068 (find units in Sean’s function), 25% - DOY: 153, 50% - DOY: 171, 75% - DOY: 190… 37 days

@@

•	Climwin results

@@

### Authors' contributions

>>>>

#Figure numbers
schematic=1 #Based on D'Orangeville Figure 1
growth_pheno_by_xylem = 2  #if we include more sites, we'll make this multi-panel
rel_growth = "2a" #Based on D'Orangeville Figure 3.a), but with relative growth
cum_growth = "2b" #Similar to D'Orangeville Figure 4.a), but with cumulative relative growth
climwin = 3
pheno_Tsensitivity = 4

#SI:
#tables

#figures
climwin_rp_DOY25_SCBI = "S1"
climwin_dp_DOY25_SCBI = "S2"

@@

climwin_caption <- "Figure 3. Landscapes of relationships between the day of year on which 25% of annual growth is achieved (DOY_25) and temperature in prior weeks for ring- and diffuse-porous trees. Shown is climwin output indicating the change in AIC relative to a null model (first panel) and linear coefficients (second panel). Window Open and Window Close indicate number of weeks prior to DOY_25 (ring-porous: DATE; diffuse-porous: DATE). Black boxes indicate the optimal window (i.e., that with lowest dAIC)."

@@

climwin_rp_DOY25_SCBI_short_caption <- "Figure S1. Full climwin output for DOY 25 for ring porous species at SCBI."
climwin_dp_DOY25_SCBI_short_caption <- "Figure S1. Full climwin output for DOY 25 for diffuse porous species at SCBI."
```

@@

*Fitting growth curves*

@@

*Determining optimal climate windows*

@@

@@

*(Numbers in bold will change. If we bring in HF and/or SERC, we should create a table, rather than trying to list everything in the text.)*

Across all trees and years, 25% of annual growth was achieved on **May 9** ($DOY_{25}$=**129**), 50% on **June 6** ($DOY_{50}$=**157**), and 75% on **July 3** ($DOY_{75}$=**184**), for an average peak growing season length of **56** days. Maximum growth rate occurred *just one day after $DOY_{50}$* on **June 7** ($DOY_{max}$=**158**).

Growth pheonology differed between ring- and diffuse- porous species, with ring-porous species having an earlier start to growth, with growth spread out over a longer growing season (Fig. `r growth_pheno_by_xylem`).
For ring-porous trees, on average, 25% of annual growth was achieved on **April 23** ($DOY_{25}$=**113**), 50% on **May 27** ($DOY_{50}$=**147**), and 75% on **June 30** ($DOY_{75}$=**181**), for an average peak growing season length of **68** days. Maximum growth rate occurred *on $DOY_{50}$* and averaged .048 **mm day^-1^ (?)**. 
For diffuse-porous trees, on average, 25% of annual growth was achieved on **June 2** ($DOY_{25}$=**153**), 50% on **June 20** ($DOY_{50}$=**171**), and 75% on **July 9** ($DOY_{75}$=**190**), for an average peak growing season length of **37** days. Maximum growth rate occurred *just one day after $DOY_{50}$* on **June 21** ($DOY_{max}$=**172**) and averaged .068 **mm day^-1^ (?)**.

@@

•	Climwin results (Figs. `r climwin`, `r climwin_rp_DOY25_SCBI`, `r climwin_dp_DOY25_SCBI`)

```{r climwin, out.width="100%", echo=FALSE, fig.align="center", fig.cap= cum_growth_caption}
# Created in RScripts/additional_figures.R
knitr::include_graphics("tables_figures/climwin.png")
```

@@

### Author Contributions

### Supporting Information

`r climwin_rp_DOY25_SCBI_short_caption`

`r climwin_dp_DOY25_SCBI_short_caption`
